---
title: "Beta-Binomial prior elicitation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Beta-Binomial prior elicitation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Live demo

[Open this example in Shinylive](https://jkunst.com/shinymodist/demos/bayes-beta-binomial/)

The app runs entirely in the browser with webR; no local R installation is
required for the demo.


A Beta input provides a direct way to shape a prior over a probability.

If the prior is

\[
p \sim \mathrm{Beta}(\alpha, \beta)
\]

and we observe \(x\) successes in \(n\) Bernoulli trials, the conjugate
posterior is

\[
p \mid x,n \sim
\mathrm{Beta}(\alpha + x, \beta + n - x).
\]

The example uses `bslib::page_sidebar()`: the editable prior and trial
controls live in the sidebar, while the prior/posterior plot is shown in a
`bslib::card()`.

The Shiny input provides the current `alpha` and `beta` values:

```{r, eval=FALSE}
bslib::sidebar(
  modist_input(
    "prior",
    family = "beta",
    value = list(alpha = 2, beta = 2)
  ),
  sliderInput("n", "Trials", min = 1, max = 100, value = 20),
  sliderInput("x", "Successes", min = 0, max = 20, value = 12)
)
```

The prior and posterior curves need only base R's `dbeta()`.

Run the complete example with:

```{r, eval=FALSE}
shiny::runApp(
  system.file("examples/bayes-beta-binomial", package = "shinymodist")
)
```
