---
title: "Distribution gallery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Distribution gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`shinymodist` exposes the distribution families provided by the bundled
modist version through the same input API.

The gallery is primarily a visual and responsive QA example: it places all
families in a grid and also shows a Normal input in a narrow 300 px sidebar.

```{r, eval=FALSE}
modist_input("normal", family = "normal")
modist_input("beta", family = "beta")
modist_input("studentt", family = "studentt")
modist_input("weibull", family = "weibull")
```

Run the complete gallery with:

```{r, eval=FALSE}
shiny::runApp(
  system.file("examples/gallery", package = "shinymodist")
)
```

By default, height remains responsive to the available width. For constrained
layouts, an explicit CSS height can be supplied:

```{r, eval=FALSE}
modist_input(
  "dist",
  family = "normal",
  height = "180px"
)
```

The default remains unchanged when `height = NULL`. Text sizing is intentionally
opinionated and not exposed as R arguments; advanced applications can override
the package CSS if needed.
